The Promise that R makes

### 2019-03-08 report/report.Rmd
Add reduction, summarization, visualiation and reporting for promises

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_distribution_by_category")
```

```{r echo = FALSE}
show_table("promise_distribution_by_category")
```

@@

>>>>

@@

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_category")
```

```{r echo = FALSE}
show_table("promise_count_by_category")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_promise_count_by_expression_type")
```

```{r echo = FALSE}
show_table("argument_promise_count_by_expression_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("non_argument_promise_count_by_expression_type")
```

```{r echo = FALSE}
show_table("non_argument_promise_count_by_expression_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_promise_count_by_value_type")
```

```{r echo = FALSE}
show_table("argument_promise_count_by_value_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("non_argument_promise_count_by_value_type")
```

```{r echo = FALSE}
show_table("non_argument_promise_count_by_value_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_promise_count_by_creation_scope")
```

```{r echo = FALSE}
show_table("argument_promise_count_by_creation_scope")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("non_argument_promise_count_by_creation_scope")
```

```{r echo = FALSE}
show_table("non_argument_promise_count_by_creation_scope")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_promise_count_by_forcing_scope")
```

```{r echo = FALSE}
show_table("argument_promise_count_by_forcing_scope")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("non_argument_promise_count_by_forcing_scope")
```

```{r echo = FALSE}
show_table("non_argument_promise_count_by_forcing_scope")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_promise_count_by_dispatch_type")
```

```{r echo = FALSE}
show_table("argument_promise_count_by_dispatch_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_force_count")
```

```{r echo = FALSE}
show_table("promise_count_by_force_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_metaprogram_count")
```

```{r echo = FALSE}
show_table("promise_count_by_metaprogram_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_value_lookup_count")
```

```{r echo = FALSE}
show_table("promise_count_by_value_lookup_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_value_assign_count")
```

```{r echo = FALSE}
show_table("promise_count_by_value_assign_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_expression_lookup_count")
```

```{r echo = FALSE}
show_table("promise_count_by_expression_lookup_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_expression_assign_count")
```

```{r echo = FALSE}
show_table("promise_count_by_expression_assign_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_environment_lookup_count")
```

```{r echo = FALSE}
show_table("promise_count_by_environment_lookup_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_environment_assign_count")
```

```{r echo = FALSE}
show_table("promise_count_by_environment_assign_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_direct_self_scope_mutation")
```

```{r echo = FALSE}
show_table("promise_count_by_direct_self_scope_mutation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_indirect_self_scope_mutation")
```

```{r echo = FALSE}
show_table("promise_count_by_indirect_self_scope_mutation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_direct_lexical_scope_mutation")
```

```{r echo = FALSE}
show_table("promise_count_by_direct_lexical_scope_mutation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_indirect_lexical_scope_mutation")
```

```{r echo = FALSE}
show_table("promise_count_by_indirect_lexical_scope_mutation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_direct_non_lexical_scope_mutation")
```

```{r echo = FALSE}
show_table("promise_count_by_direct_non_lexical_scope_mutation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_indirect_non_lexical_scope_mutation")
```

```{r echo = FALSE}
show_table("promise_count_by_indirect_non_lexical_scope_mutation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_direct_self_scope_observation")
```

```{r echo = FALSE}
show_table("promise_count_by_direct_self_scope_observation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_indirect_self_scope_observation")
```

```{r echo = FALSE}
show_table("promise_count_by_indirect_self_scope_observation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_direct_lexical_scope_observation")
```

```{r echo = FALSE}
show_table("promise_count_by_direct_lexical_scope_observation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_indirect_lexical_scope_observation")
```

```{r echo = FALSE}
show_table("promise_count_by_indirect_lexical_scope_observation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_direct_non_lexical_scope_observation")
```

```{r echo = FALSE}
show_table("promise_count_by_direct_non_lexical_scope_observation")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_count_by_indirect_non_lexical_scope_observation")
```

```{r echo = FALSE}
show_table("promise_count_by_indirect_non_lexical_scope_observation")
```
